Object-Oriented Internet - Azure Interoperability

### 2020-12-06 Latex/Manuscript.tex
Final review of the latex text #37
- MP review finished.

Using the data type definition to describe information interchange between communicating parties allows:

\begin{itemize}
      \item Development against a type definition of the user interface
      \item Implementation of the functionality of the bitstreams conversion in advance
\end{itemize}

@@

\todo{vendor products and cannot be recognized as a generic solution that can be used to connect to other clouds at the same time}

@@

From the analysis covered by the Sect. \ref*{subs.architecture} it is concluded that the \textbf{embedded gateway} archetype best suits all requirements described above. It relaxes most of the issues related to \textbf{direct interconnection} and solutions inferred from the middleware concept, i.e. \textbf{edge device} - remote cloud agent and \textbf{field level gateway} - a dedicated custom agent. The generic domain model for the proposed interconnection archetype is presented in the Fig.~\ref*{figure1.StrategyDomainModel}. We have highlighted that to promote the separation of concern design principle, the gateway functionality should be implemented as a self-contained dedicated software part embedded in the core \textit{Networking} service of the \textit{Cyber-physical\ node}. Main functionality of this component is to transfer process data between \textit{Cyber-physical\ network} using \textit{Networking} services of an existing \textit{Cyber-physical\ node} and \textit{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.

@@

The described results prove that the \textbf{embedded gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard. It is worth stressing that there is no dependency on the Client/Server session-oriented relationship. This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server. In the proposed approach the cloud interoperability is obtained by implementing a dedicated part employing out-of-band communication only without dependency on the OPC UA functionality at all. It is worth stressing that the gateway functionality is implemented as a part - composable to the whole without programming skills. Because the part is composed at the runtime it makes it possible to modify its functionality later after releasing the library or even deploying the application program in the production environment.

>>>>

Using the data type definitions to describe information interchange between communicating parties allows:

\begin{itemize}
      \item development against a type definition of the user interface
      \item implementation of the functionality of the bitstreams conversion in advance
\end{itemize}

@@

@@

From the analysis covered by the Sect. \ref*{subs.architecture} it is concluded that the \textbf{embedded gateway} archetype best suits all requirements described above. It relaxes most of the issues related to \textbf{direct interconnection} and solutions inferred from the middleware concept, i.e. \textbf{edge device} - remote cloud agent and \textbf{field level gateway} - a dedicated custom agent. Additionally, it could be used to connect to many independent clouds at the same time. The generic domain model for the proposed interconnection archetype is presented in the Fig.~\ref*{figure1.StrategyDomainModel}. We have highlighted that to promote the separation of concern design principle, the gateway functionality should be implemented as a self-contained dedicated software part embedded in the core \textit{Networking} service of the \textit{Cyber-physical\ node}. Main functionality of this component is to transfer process data between \textit{Cyber-physical\ network} using \textit{Networking} services of an existing \textit{Cyber-physical\ node} and \textit{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.

@@

The described results prove that the \textbf{embedded gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard. It is worth stressing that there is no dependency on the Client/Server session-oriented relationship. This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server. The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to embed the \textbf{embedded gateway} component into the OPC UA Client or Server to get connected with the cloud in case of the interactive relationship.

In the proposed approach the cloud interoperability is obtained by implementing a dedicated part employing out-of-band communication only without dependency on the OPC UA functionality at all. It is worth stressing that the gateway functionality is implemented as a part - composable to the whole without programming skills. Because the part is composed at the runtime it makes it possible to modify its functionality later after releasing the library or even deploying the application program in the production environment.
